---
title: "Student Sit in"
author: "Melissa Markakis"
date: "10/26/2019"
output: 
  html_document:
    toc: true
    number_sectons: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# ONE SHOT assignment!
this is an extra credit assignment, must be completed Monday Oct 28, turn-in closes at midnight!

## Problem statement: 
Students at UCD- is there a relation between where one sits and one's major? 

## Introduction  

<!-- where is the data found?  Is this an experiment or an observational study?  !-->

Data from this study came from... 

The data came from a study of 173 student at UC Davis.


```{r include=FALSE, echo=FALSE}
library(tigerstats)
data(ucdavis1)

```

$H_0$: there is no relationship between one's major and where one sits in a class   
$H_A$: where one sits in class and one's major are related  

<!-- Get the data: !-->



The names in the data frame are Seat and class.  

```{r echo=FALSE}
UCDdataframe = data.frame(seat=ucdavis1$Seat, major=ucdavis1$class, data=ucdavis1)
names(UCDdataframe)
```
## Methods

<!--  describe analysis methods here 
what are the variable types, and indicate gaphical, numerical, and inferential methods appropriate
for this question  !--> 
 
 Both variables are categorical. We will do a bar chart for graphical data. For numerical methods we use a tables chart. Finally, we use a Chi- Squared test for our inferential method.  

## Data summary

**Graphical summary**


```{r}
barchartGC(~Seat+class, data=ucdavis1, main = 'Seat v.s Class', type = 'percent', xlab = ' Seat')
```

The bar chart suggests that there is no connection between where one sits and ones major. Liberal Arts majoring students appear to sit almost equally in the front, middle and back of the class but do prefer the front just a little bit more. Non-Liberal Arts student appear to prefer to sit in the back but are nearly equal accross the bar.  


**Numerical summary**


```{r}
tab1 = xtabs(~Seat+class, data=ucdavis1)
rowPerc(tab1)
```

The numerical tables Summary suggests that Liberal Arts students prefer to sit more in the front of the classroom but the non liberal arts students appear to prefer the back of the classroom.  

## Inferential Results


```{r}
chisqtestGC(tab1)
```


The p-value is 0.2173 > 0.05 suggest that there is no connection between where one sits and ones major.   

## Results and conclusions

<!-- explain-- is there evidence that certain majors tend to sit in particular areas of the class?  Can the results of this test be generalized to all majors in all universities? !-->


The p-value for the Chisq test is 0.2173 > 0.05 so we fail to reject the null hypothesis and conclude do we have enpugh evidence to support the contention that ones major and where one sits is related. It appears ones choise of seating is not related to ones choice of major.  
<!--
push results to your github account, turn in the URL

--OR--

If you did not fork my repo to your github account,
create a repository in your github account for this project, get the URL for that repo and 
(in the terminal window..)

$git remote add origin URL_of_your_github_repo
$git push -u origin master

!-->